---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aRts

<!-- badges: start -->
<!-- badges: end -->

Sometimes data science methods for data collection and data processing not only 
produce meaningful results, they also can be used to create just nice looking 
plots. This package is a very personal collection of artwork that I have been 
working on over the last couple of years. 

## Installation

Currently there is no version on `CRAN`. You can install the development version 
of `aRts` from github using:

```{r setup, eval = FALSE}
install.packages("remotes")
remotes::install_github("hewag1975/aRts")
library(aRts)
```


## Content

Currently, the packages contains code and documentation for 

* making paintings from photographs using the [supercells](https://github.com/Nowosad/supercells/)-package
* ...

For every workflow there is a vignette available describing the idea, the process and the results using some examples.


## Kudos

Inspiration for these artwork came from many other R-packages and their authors, namely [Jakub Nowosad](https://github.com/Nowosad), ...
