---
title: "Create a painting from an image"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE
  # , comment = "#>"
  , out.width = "100%"
)
```


## Superpixels

The concept of SLIC superpixels is well explained in the package documentation of the 
[supercells package](https://github.com/Nowosad/supercells). Basically, 
superpixels segment an image into contiguous parts with similar color values. 
The intention of the [supercells package](https://github.com/Nowosad/supercells) 
is to apply this concept to a variety of spatial data. However, it can likewise 
be applied to ordinary photographs to create painting- or cartoon-like image 
representations. 

There are also a few other R-packages available that do similar things but have 
not been evaluated here:

* [imager](https://github.com/dahtah/imager)
* [SuperpixelImageSegmentation](https://github.com/mlampros/SuperpixelImageSegmentation)
* [OpenImageR](https://mlampros.github.io/OpenImageR/articles/Image_segmentation_superpixels_clustering.html)


## Example

The `aRts` packages comes along with a selection of images that can be used for 
exploration.

```{r pkg, message = FALSE}
library(stars)
library(sf)
library(aRts)

ifl = system.file(
  paste0("img/", c("autumn", "lake", "mountains_1", "mountains_2"), ".jpg")
  , package = "aRts"
)
ifl
```

In order to apply the `supercells` implementation of superpixels, we need to 
submit our images in a spatial format, either as `stars` or as `spatRaster` 
object. 

```{r imp}
img = read_stars(ifl[[1]])
img
st_crs(img)
```

Of course our image at this point in time does not contain 

We can vary the reuqested number of supercells, see the effect:

```{r}
ptg = lapply(
  c(500, 1000, 2000, 5000)
  , FUN = \(i) painting(img, k = i)
)

par(mfrow = c(2, 2))
for (i in 1:4) plot(ptg[[i]])
```

Likewise we can play with compactness:

```{r}
ptg = lapply(
  c(1, 10, 50, 100)
  , FUN = \(i) painting(img, k = 2500, compactness = i)
)

par(mfrow = c(2, 2))
for (i in 1:4) plot(ptg[[i]])
```

Or the average function:

```{r}
ptg = lapply(
  c("mean", "median", "max", "sd")
  , FUN = \(i) {
    painting(
      img
      , k = 2500
      , compactness = 10
      , avg_fun = eval(str2expression(i))
    )
  }
)

par(mfrow = c(2, 2))
for (i in 1:4) plot(ptg[[i]])
```

## Create paintings

Create a painting using the default settings.

```{r}
ptg = lapply(
  img
  , FUN = painting
)

ptg[[1]]
class(ptg[[1]])
```

Plot original image and painting side by side.

```{r asp, include = FALSE}
ratio = lapply(img, FUN = \(i) dim(i)[2] / (2 * dim(i)[1]))
```

```{r lake, fig.asp = ratio[[1]]}
par(mfrow = c(1, 2))
plot(img[[1]], rgb = 1:3, main = "", reset = FALSE, useRaster = TRUE)
plot(ptg[[1]])
```

```{r mountains, fig.asp = ratio[[2]]}
par(mfrow = c(1, 2))
plot(img[[2]], rgb = 1:3, main = "", reset = FALSE, useRaster = TRUE)
plot(ptg[[2]])
```


## Export results

The `sf_paint` object is basically a spatial class with a number of polygons 
delineating areas of similar color compsition on the image. To save the paiting 
to disk, you can use the plot device and .

```{r exp, eval = FALSE}
jpeg(
  "~/lake_painting.jpg"
  , width = dim(img[[1]])[1]
  , height = dim(img[[1]])[2]
  , units = "px"
)
plot(ptg[[1]])
dev.off()
```


## Bulk processing

```{r imp}
img = lapply(ifl, FUN = read_stars)
ptg = lapply(img, FUN = painting, k = 2500, compactness = 50)

par(mfrow = c(2, 2))
lapply(ptg, FUN = plot)

mapply(
  \(img, ptg, ofl){
    jpeg(
      paste0("~/", ofl)
      , width = dim(img)[1]
      , height = dim(img)[2]
      , units = "px"
    )
    plot(ptg)
    dev.off()
  }
  , img = img
  , ptg = ptg
  , ofl = paste0("paint_", basename(ifl))
)

```






```{r, eval = FALSE}
ifl = system.file(
  paste0("img/", c("autumn", "lake", "mountains_1", "mountains_2"), ".jpg")
  , package = "aRts"
)
ifl

library(OpenImageR)
aut = readImage(ifl[1])

aut_slic = superpixels(
  input_image = aut,
  method = "slic",
  superpixel = 200, 
  compactness = 20,
  return_slic_data = TRUE,
  return_labels = TRUE, 
  write_slic = "", 
  verbose = TRUE
)

par(mfrow=c(1,2), mar = c(0.2, 0.2, 0.2, 0.2))

plot_slic = OpenImageR::NormalizeObject(aut_slic$slic_data)
plot_slic = grDevices::as.raster(plot_slic)
graphics::plot(plot_slic)

plot_slico = OpenImageR::NormalizeObject(res_slico$slic_data)
plot_slico = grDevices::as.raster(plot_slico)
graphics::plot(plot_slico)


library(magick)
aut = image_read(ifl[1])
plot(aut)
```


