---
title: "painting"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```


## Make a paining from a photo

The package comes with a few example image which can be used for exploration. 
All the included images have been converted to an object of class `stars`. 

```{r}
library(stars)
library(sf)
library(aRts)
data(autumn)
class(autumn)
autumn
```

As you can see, the image has three dimensions (`r dim(autumn)`) and also has a 
CRS assigned (`r sf::st_crs(autumn)$input`). Now, this does not make sense for a 
photo but is just make it work. 

Create a painting using the default settings.

```{r}
plot(autumn, rgb = 1:3, main = "", reset = FALSE, useRaster = TRUE)
autumn_paint = painting(autumn)
autumn_paint
class(autumn_paint)
```

Plot original image and painting side by side.

```{r}
par(mfrow = c(1, 2))
plot(autumn, rgb = 1:3, main = "", reset = FALSE, useRaster = TRUE)
plot(autumn_paint)
```

Save the image to disk.

```{r}
# plot(sc)
# class(sc)
# jpeg(
#     "img/fichtel_sc.jpg"
#     , width = dim(img)[1]
#     , height = dim(img)[2]
#     , units = "px"
# )
# plot(
#     sf::st_geometry(sc)
#     , border = NA
#     , col = sc$col
# )
# dev.off()
```


## Image preparation

```{r, eval = FALSE}
ifl = "~/Pictures/images/pic_001.jpg"
autumn = stars::read_stars(ifl)
names(autumn) = "Autumn forest"
```



```{r}
data(mountains)
mountains_paint = painting(mountains)

par(mfrow = c(1, 2))
plot(mountains, main = "", rgb = 1:3, reset = FALSE, useRaster = TRUE)
plot(mountains_paint)
```

